A Java Framework For Embarrassingly Parallel Problems

### 2013-12-10 paper/paper.tex
directory output

We evaluated the convenience and performance of the framework on two different
applications: the Ka/Ks Calculator and two different sequence clustering
algorithms, USEARCH and ocutupus. In all cases, we compared the framework based
application with the original using different data partitions and different
thread counts.

\subsection{Ka/Ks Calculator}
TODO: Reword when redone
Ka/Ks Calculator was run through the framework with ten different samples, each
containing sixteen units of work. Each sample was run by the framework thread
counts, starting at 1 and increasing by powers of two until the 100\% processor
usage (16 processors). These tests were run with minimal other activity on the
server.

@@

\subsection{uClust}

TODO: Place holder text

@@

TODO: Place holder text

@@

TODO: First paragraph should summarize performance: its clear that framework
provides simple and effective module for adding parallelism to a class of
file-oriented EP apps. More self praise.

@@

\begin{thebibliography}{1}
\bibitem{history}
Moler, Cleve. ``\emph{Matrix Computation on Distributed Memory Multiprocessors."
}, Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
T. Heath. Philadelphia: SIAM, 1986. N. pag. Print.
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{Ka/Ks Calculator: 
calculating Ka and Ks through model selection and model averaging},
Genomics Proteomics Bioinformatics, November 2006.
\bibitem{cluster}
Rua, Xu, Wunsch, Donald II, \emph{Survey of Clustering Algorithms},
IEEE Transactions on Neural Networks VOL. 16, NO. 3, MAY 2005
\bibitem{cloud}
Crap, crap and Crap
\end{thebibliography}

>>>>

We evaluated the convenience and performance of the framework on two different
applications: the Ka/Ks Calculator and a sequence clustering algorithms,
ocutupus. In all cases, we compared the framework based application with the
original using different data partitions and different thread counts.

\subsection{Ka/Ks Calculator}
Ka/Ks Calculator was run through the framework with five different samples, each
containing sixteen units of work. Each sample was run by the framework thread
counts, starting at 1 and increasing by multiple of two until the runtimes
leveled off. The samples were then all run again at 100\% processor usage (16
processors). These tests were run with minimal other activity on the server.

@@

@@

A version of octupus was also run through the framework and was tested against
two different sized data sets. Both sets were first clustered at 90\% similarity
and the resulting clusters were used as the input for the framework's run, which
is for 97\% similarity. The framework in this case was just run at four and
eight threads and Figure \ref{fig:octugraph} shows that the running the
framework once again provides a benefit for the user.

\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{experiment/outoctu.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:octugraph}
\end{figure}

@@

It is clear that the framework provides an effective yet simple to use module to
add parallelism to a specific class of file-oriented embarrassingly parallel
problems. Two sentences with specifics from the graphs. More self-praise

@@

\begin{thebibliography}{1}
\bibitem{kaks}
Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{Ka/Ks Calculator: 
calculating Ka and Ks through model selection and model averaging},
Genomics Proteomics Bioinformatics, November 2006.
\bibitem{cloud}
Crap, crap and Crap
\end{thebibliography}
